Twists of supersymmetric gauge theories

### 2019-08-17 paper.tex
Minor wording changes
Definition of dimensional reduction

>>>>

\subsection{Dimensional Reduction, take 2}

\begin{definition}
A classical field theory $(E_N, Q_N, \omega_N, I_N)$ on a manifold $N$ is a {\bf dimensional reduction} of the classical field theory $(E_M, Q_M, \omega_M, I_M)$ on a manifold $M$ if we are given the following data:
\begin{itemize}
\item A submersion $p\colon M\rightarrow N$ equipped with a fiberwise volume form, i.e. an isomorphism $p^*\Dens_N\cong \Dens_M$.

\item An isomorphism $p^* E_N\cong E_M$.
\end{itemize}
These data are required to satisfy the following conditions:
\begin{itemize}
\item The diagram
\[
\xymatrix{
p^* E_N\otimes p^* E_N \ar^{\omega_N}[r] \ar^{\sim}[d] & p^*\Dens_N[-1] \ar^{\sim}[d] \\
E_M\otimes E_M \ar^{\omega_M}[r] & \Dens_M[-1]
}
\]
is commutative.

\item The diagram
\[
\xymatrix{
\cE_N \ar^{Q_N}[r] \ar^{p^*}[d] & \cE_N[1] \ar^{p^*}[d] \\
\cE_M \ar^{Q_M}[r] & \cE_M[1]
}
\]
is commutative.

\item Under the map $p^*\colon \cE_N\rightarrow \cE_M$ we have $p^* I_M = I_N$.
\end{itemize}
\end{definition}
